Algorithm explanation

### 2013-04-21 article/algo.tex
Modifying the least element to the greatest element

\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{listings}
\usepackage{stmaryrd}
\usepackage{syntax}

@@

Given an acyclic Horn graph (or called a Horn DAG), we define the
relation $u <^+ v$ as follows.
\[ u <^+ v \Longleftrightarrow \exists \theta. (u,v,\theta) \in E \]
By the assumption that $G$ is acyclic, $<^+$ is a well-founded
relation. We assume without loss of generality that $V$ contains the
least element $v_\bot$ with respect to $<^+$; otherwise we can always
implicitly assume $\varphi(v_\bot) = 0 \leq -1$.

@@

\begin{align*}
C_v =
\bigcup_{(u,v) \in E} C_u & \cup
\left\lbrace
 \mathbf{a}_v = \sum_{(u,v) \in E} \mathbf{a}_u,
 b_v \geq \sum_{(u,v) \in E} b_u
\right\rbrace \cup
\\
& \begin{cases}
\emptyset
& \mbox{if } \varphi(v) = P(\mathbf{x}) \\
\left\lbrace
 \lambda_v \geq 0, \mathbf{a}_v = \lambda_v \mathbf{a}_0,
 b_v = \lambda_v b_0
\right\rbrace
& \mbox{if } \varphi(v) = \mathbf{a}_0 \mathbf{x} \leq b_0
\end{cases}
\end{align*}

Given a set of maximal nodes
$V_\top = \left\lbrace v \in V \middle| \neg(\exists v'. v <^+ v') \right\rbrace$,
any model $\sigma$ to the constraint
$C_{V_\top} = \bigwedge_{v \in V_{\top}} C_v$ gives a
simple solution for $G$ if $C_{V_\top}$ is satisfiable, i.e., we
should have:

\begin{quote}
If $\models \sigma(C_{V_\top})$, then $\rho$ defined by
\begin{align*}
 \rho = \left\lbrace
  \left( P, \sigma(\mathbf{a}_v \mathbf{x} \leq b_v) \right) \middle|
  \forall v \in V. \varphi(v) = P(\mathbf{x})
 \right\rbrace
\end{align*}
is a solution of $G$.
\end{quote}

If $C_{V_\top}$ is unsatisfiable, there are two possibilities for them.

@@

Obtaining $G'$ after the transformation above, if $C_{v_\bot}$ becomes
satisfiable, a solution $\rho$ to $G$ is given by using solution
$\rho'$ to $G'$:

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{listings}
\usepackage{stmaryrd}
\usepackage{syntax}

@@

Given an acyclic Horn graph (or called a Horn DAG), we define the
relation $u <^+ v$ as follows.
\[ u <^+ v \Longleftrightarrow \exists \theta. (u,v,\theta) \in E \]
By the assumption that $G$ is acyclic, $<^+$ is a well-founded
relation. We assume without loss of generality that $V$ contains the
greatest element $v_\bot$ with respect to $<^+$; otherwise we can
always implicitly assume $\varphi(v_\bot) = 0 \leq 0$.

@@

\begin{align*}
C_v = & \bigcup_{(u,v) \in E} C_u
\\
& \cup \begin{cases}
\emptyset
& \mbox{if } \nexists u. u <^+ v \\
\left\lbrace
 \mathbf{a}_v = \sum_{u <^+ v} \mathbf{a}_u,
 b_v \geq \sum_{u <^+ v} b_u
\right\rbrace
& \mbox{otherwise}
\end{cases}
\\
& \cup \begin{cases}
\emptyset
& \mbox{if } \varphi(v) = P(\mathbf{x}) \\
\left\lbrace
 \lambda_v \geq 0, \mathbf{a}_v = \lambda_v \mathbf{a}_0,
 b_v = \lambda_v b_0
\right\rbrace
& \mbox{if } \varphi(v) = \mathbf{a}_0 \mathbf{x} \leq b_0
\end{cases}
\end{align*}

Any model $\sigma$ to the constraint $C_{v_\bot}$ gives a simple
solution for $G$ if $C_{v_\bot}$ is satisfiable, i.e., we should have:

\begin{quote}
If $\models \sigma(C_{v_\bot})$, then $\rho$ defined by
\begin{align*}
 \rho = \left\lbrace
  \left( P, \sigma(\mathbf{a}_v \mathbf{x} \leq b_v) \right) \middle|
  \forall v \in V. \varphi(v) = P(\mathbf{x})
 \right\rbrace
\end{align*}
is a solution of $G$.
\end{quote}

If $C_{v_\bot}$ is unsatisfiable, there are two possibilities for them.

@@

Obtaining $G'$ after the transformation above, if $C_{v_\top}$ becomes
satisfiable, a solution $\rho$ to $G$ is given by using solution
$\rho'$ to $G'$:
